\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
Fixed section refs in intro

After exploring the state of the art \ref{sec:related_work} and explaining
the architecture of AORTA \ref{sec:arch} as well as its use of OSM \ref{sec:map},
we will describe simulation in AORTA \ref{sec:simulation} and how to extend it
\ref{sec:config}, concluding with an example experiment \ref{sec:results}.
In this final experiment, AORTA shows the benefits of an AIM-inspired
\cite{JAIR08-dresner} reservation intersection policy over traditional
traffic signals and stop signs.

>>>>

After exploring the state of the art in section \ref{sec:related_work} and explaining
the architecture of AORTA (section \ref{sec:arch}) as well as its use of OSM (section \ref{sec:map}),
we will describe simulation in AORTA and how to extend it in sections \ref{sec:simulation} and
\ref{sec:config} respectively. We conclude with an example experiment in section \ref{sec:results}.
In this final experiment, AORTA shows the benefits of an AIM-inspired
\cite{JAIR08-dresner} reservation intersection policy over traditional
traffic signals and stop signs.
